High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2020-11-03 paper/main.tex
edits made while text banking-- review carefully

\begin{abstract}
  Our thoughts arise from coordinated patterns of interactions between
  brain structures that change with our ongoing experiences.
  High-order dynamic correlations in neural activity patterns reflect
  different subgraphs of the brain's connectome that display
  homologous lower-level dynamic correlations.  We tested the
  hypothesis that high-level cognition is reflected in high-order
  dynamic correlations in brain activity patterns.  We developed an
  approach to estimating high-order dynamic correlations in timeseries
  data, and we applied the approach to neuroimaging data collected as
  human participants either listened to a ten-minute story, listened
  to a temporally scrambled version of the story, or underwent a
  resting state scan.  We trained across-participant pattern
  classifiers to decode (in held-out data) when in the session each
  neural activity snapshot was collected.  We found that classifiers
  trained to decode from high-order dynamic correlations yielded the
  best performance on data collected as participants listened to the
  (unscrambled) story.  By contrast, classifiers trained to decode
  data from scrambled versions of the story or during the resting
  state scan yielded the best performance when they were trained using
  first-order dynamic correlations or non-correlational activity patterns.  We
  suggest that as our thoughts become more complex, they are reflected
  in higher-order patterns of dynamic network interactions throughout
  the brain.
\end{abstract}

@@

We used a subset of the story listening and rest data to train
across-participant classifiers to decode listening times using a blend
of neural features (comprising neural activity patterns, as well as
different orders of dynamic correlations between those patterns that
were inferred using our computational framework).  We found that both
the PCA-based and eigenvector centrality-based approaches yielded
neural patterns that could be used to decode accurately (i.e., well
above chance).  Both approaches also yielded the best decoding
accuracy for data collected during (intact) story listening when
high-order (PCA: second-order; eigenvector centrality: fourth-order)
dynamic correlation patterns were included as features.  When we
trained classifiers on the scrambled stories or resting state data,
only lower-order dynamic patterns were informative to the decoders.
Taken together, our results indicate that high-level cognition is
supported by high-order dynamic patterns of communication between
brain structures.

>>>>

\begin{abstract}
  Our thoughts arise from coordinated patterns of interactions between
  brain structures that change with our ongoing experiences.
  High-order dynamic correlations in neural activity patterns reflect
  different subgraphs of the brain's connectome that display
  homologous lower-level dynamic correlations.  We tested the
  hypothesis that high-level cognition is reflected in high-order
  dynamic correlations in brain activity patterns.  We developed an
  approach to estimating high-order dynamic correlations in timeseries
  data, and we applied the approach to neuroimaging data collected as
  human participants either listened to a ten-minute story or listened
  to a temporally scrambled version of the story.  We trained
  across-participant pattern classifiers to decode (in held-out data)
  when in the session each neural activity snapshot was collected.  We
  found that classifiers trained to decode from high-order dynamic
  correlations yielded the best performance on data collected as
  participants listened to the (unscrambled) story.  By contrast,
  classifiers trained to decode data from scrambled versions of the
  story yielded the best performance when they were trained using
  first-order dynamic correlations or non-correlational activity
  patterns.  We suggest that as our thoughts become more complex, they
  are reflected in higher-order patterns of dynamic network
  interactions throughout the brain.
\end{abstract}

@@

We used a subset of the story listening and rest data to train
across-participant classifiers to decode listening times using a blend
of neural features (comprising neural activity patterns, as well as
different orders of dynamic correlations between those patterns that
were inferred using our computational framework).  We found that both
the PCA-based and eigenvector centrality-based approaches yielded
neural patterns that could be used to decode accurately (i.e., well
above chance).  Both approaches also yielded the best decoding
accuracy for data collected during (intact) story listening when
high-order (PCA: second-order; eigenvector centrality: fourth-order)
dynamic correlation patterns were included as features.  When we
trained classifiers on the scrambled stories or resting state data,
only (relatively) lower-order dynamic patterns were informative to the decoders.
Taken together, our results indicate that high-level cognition is
supported by high-order dynamic patterns of communication between
brain structures.
